Insert the article title here

### 2018-04-30 writeup/manuscript.tex

\subsubsection{Split-half Array Search}
Our results are broadly in line with \cite{nowakowsak2017}. The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b). We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reaction times. Furthermore, test-retest reliability appears to be reasonable, with correlations of around $r = 0.78$ (the value of $r = 0.71$ or easy targets is slightly lower, likely due to the restricted range).

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
\caption{Correlation between the two sessions of the \textit{split-half} paradigm for (a)  accuracy (TP-heterogeneous), (b) reaction times and (c) search strategy. (d) initial search strategy correlates with reaction times in both sessions. Each point represents a participant and the error-bars indicate 95\% confidence intervals.}
\label{fig:splithalf_summary}
\end{figure}

We can also look at the initial search strategies adopted by our participants \ref{fig:splithalf_summary}(c, d). Again, we see large and stable individual differences across the two sessions. More importantly, as with \cite{nowakowsak2017}, we see that the search strategies give a good correlation with reaction times.

>>>>

\subsubsection{Split-half Array Search}
Our results are broadly in line with \cite{nowakowsak2017}. The correlation between accuracy and reaction times between the two sessions is shown in Figure \ref{fig:splithalf_summary}(a, b). We can clearly see that there are large differences from one participant to the next in terms of both the proportion of hard targets found, and reaction times. Furthermore, test-retest reliability appears to be reasonable, with Pearson's $r \in [0.65-0.86]$ ($95\%$ confidence interval) for accuracy in finding targets on the hard heterogeneous half of the display. We get similar scores for the correlation between sessions \textit{a} and \textit{b} for heterogeneous targets, ($r \in [0.66-0.87]$), homogeneous targets ($r \in [0.56-0.82]$) and target absent ($r \in [0.65-0.86]$). The reduced correlation for the homogeneous targets is likely due to the restricted range.

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
\caption{Correlation between the two sessions of the \textit{split-half} paradigm for (a)  accuracy (TP-heterogeneous), (b) reaction times and (c) search strategy. (d) initial search strategy correlates with reaction times in both sessions. Each point represents a participant and the error-bars indicate 95\% confidence intervals.}
\label{fig:splithalf_summary}
\end{figure}

We can also look at the initial search strategies adopted by our participants \ref{fig:splithalf_summary}(c, d). Again, we see large and stable individual differences across the two sessions (test-retest $r \in [0.57, 0.83]$ for the proportion of the first five saccades to the heterogeneous half of the display for target absent trials). More importantly, as with \cite{nowakowsak2017}, we see that the search strategies give a good correlation with reaction times in both session a, $r \in [0.56, 0.84]$ and session b, $r \in [0.50, 0.81]$.
